Clicks and Cliques

### 2018-12-27 papersoul.Rnw
small changes

\begin{figure}[hbpt]
<<corplot, echo=FALSE, dependson=c('data'),cache=TRUE, warning = FALSE>>=
# With Census data we want to describe communities
cors <- census.data %>% 
  gather(vars, vv, -QSB, -CCEGRP2Attached, -`CCEGRP2Not Attached` ) %>%
  group_by(vars) %>% 
  summarise(
    cor.att = cor(vv, CCEGRP2Attached, use = 'complete.obs'),
    cor.noatt = cor(vv, `CCEGRP2Not Attached`, use = 'complete.obs') ) %>% 
  filter(!is.na(cor.att), vars != 'unemployed') %>% 
  filter(rank(cor.att) %in% c(1:10, 52:61) ) %>% 
  mutate(vars =  fct_reorder(vars, cor.att) , vars = recode_factor(
      vars, 
      "av.own" = 'Aver.years.own.in.community',
      "pop100"= 'size.community', 
      "av.rent"= 'Average.years.rent.in.community',
      "ow.prop10" = 'Prop.owner.more.10.years',
      "prop.female" = 'Pro.female',
      "prop2.1worker" = 'Prop.house.2.per.1.worker',
      "prop.4.per" = 'Prop.house.4.per.or.more',
      "ren.prop10" = 'Prop.rent.more.10.years',
      "own.rate" = 'Prop.own',
      "un.rate" = 'Unemployment.rate',
      "prop1.worker" = 'Prop.1worker',
      "Bachelor.s.degree.or.higher." = 'Prop.bachelor',
      "prop3.3worker" = 'Prop.house.3.per.3.workers',
      "prop.nat.entry.90s" = 'Prop.native.entry.90s',
      "prop.nat.entry.80s" = 'Prop.native.entry.80s',
      "militar" = 'Prop.militar',
      "prop1821" = 'Prop.pop.bw.18.21',
      "prop.entry.80s" = 'Prop.new.entry',
      "prop.male" = 'Prop.male',
      "prop.2.per" = 'Prop.2perhouse')) %>% 
  gather(type, vv, -vars) %>% 
  mutate( type = factor(type, labels = c('Attached', 'Not Attached') ),
          positive = factor(sign(vv), labels = c( 'Negative', 'Positive') ) )

@@

des.cl1 %>% 
  spread(vars,value) %>% 
  select(Q25, QCE2, Q7E, Q3B, Q8D, Q8A, Q15AA, Q7L, Q9, Q3A, Q15AB, Q6A, Q3C, Q6, Q7I, Q7F, Q7K, Q8F, Q7M, Q7D, QCE1, Q7A, Q7B, Q7C, Q8C, Q8E, Q8B, Q7H, Q18, Q7G, Q24,YEAR,cl.id) %>% 
  rename( Family = Q25, Refer = QCE2, Perfect = Q7E, Children = Q3B, Leader = Q8D, Proud = Q8A, Lead.Int. = Q15AA, Talented = Q7L, Job = Q9, Meet.People = Q3A, `5year.ahead` = Q15AB, School = Q6A, Reputation = Q3C, `5year.ago` = Q6, Care = Q7I, Senior = Q7F, Economy = Q7K, Satisfaction = Q8F, Health = Q7M, Find.Job = Q7D, Parks = QCE1, 
Beauty = Q7A, Roads = Q7B, Housing = Q7C, Night.Life = Q8C, Minorities = Q8E, Inmigrants = Q8B, Gay = Q7H, Safe = Q18, Colleges = Q7G, Friends = Q24, Clusters = cl.id) %>% 
 gather(vars, value, -Clusters,-YEAR) %>% 
  ggplot(aes(x = vars, y = value, color = Clusters, shape = Clusters), size = I(3)) + labs(x = "", y = "") +  geom_point(size = I(2))  + geom_line(aes(group = Clusters)) + 
  facet_wrap(~YEAR, nrow = 3) + theme(axis.text.x = element_text(angle = 90, size = I(15)), legend.position = 'bottom' ) + scale_color_brewer(type='qual', palette='Paired')

@@

<<moving, dependson='data', echo=FALSE,results='asis', cache=FALSE>>=
soul %>% 
  mutate(Q5 = recode_factor(Q5, "(DK)" = "Non Response", 
    "(Refused)" = "Non Response",
    "Move outside of (answer from Sc) but stay in the state" = "Move from your neighborhood",
    "Move outside of this communitybut stay in the state" = "Move from your neighborhood",
    "Move to another city and state altogether" = "Move from your neighborhood",
    "Move to another neighborhood in (answer from Sc)" = "Move from your neighborhood", 
    "Move to another neighborhood in this community" = "Move from your neighborhood")) %>%  
  filter(!is.na(PROJWT)) %>% 
  mutate(pr = PROJWT/3)  %>% 
  svydesign(ids =~1, strata =~QSB, weights =~pr, data = .) %>% 
  svyby(~Q5,~CCEGRP2, design = ., svymean,keep.var = FALSE, na.rm = T) %>% 
  ftable() %>% data.frame() %>% 
  mutate( Var2 = gsub('statistic.Q5', '', Var2) ) %>% 
  spread(CCEGRP2, Freq) %>%  
  xtable(caption = 'Willingness to move outside your neighborhood', label = 'move') %>% 
  print(caption.placement = 'top')

>>>>

\begin{figure}[hbpt]
<<corplot, echo=FALSE, dependson=c('data'),cache=TRUE, warning = FALSE>>=
# With Census data we want to describe communities
cors <- census.data %>% 
  gather(vars, vv, -QSB, -CCEGRP2Attached, -`CCEGRP2Not Attached` ) %>%
  group_by(vars) %>% 
  summarise(
    cor.att = cor(vv, CCEGRP2Attached, use = 'complete.obs'),
    cor.noatt = cor(vv, `CCEGRP2Not Attached`, use = 'complete.obs') ) %>% 
  filter(!is.na(cor.att), vars != 'unemployed') %>% 
  #mutate(rr = rank(cor.att) ) %>% arrange(rr)
  filter(rank(cor.att) %in% c(1:10, 54:63) ) %>% 
  mutate(vars =  fct_reorder(vars, cor.att) , vars = recode_factor(
      vars, 
      "av.own" = 'Aver.years.own.in.community',
      "pop100"= 'size.community', 
      "av.rent"= 'Average.years.rent.in.community',
      "ow.prop10" = 'Prop.owner.more.10.years',
      "prop.female" = 'Pro.female',
      "prop2.1worker" = 'Prop.house.2.per.1.worker',
      "prop.4.per" = 'Prop.house.4.per.or.more',
      "ren.prop10" = 'Prop.rent.more.10.years',
      "own.rate" = 'Prop.own',
      "un.rate" = 'Unemployment.rate',
      "prop1.worker" = 'Prop.1worker',
      "Bachelor.s.degree.or.higher." = 'Prop.bachelor',
      "prop3.3worker" = 'Prop.house.3.per.3.workers',
      "prop.nat.entry.90s" = 'Prop.native.entry.90s',
      "prop.nat.entry.80s" = 'Prop.native.entry.80s',
      "militar" = 'Prop.militar',
      "prop1821" = 'Prop.pop.bw.18.21',
      "prop.entry.80s" = 'Prop.new.entry',
      "prop.male" = 'Prop.male',
      "prop.2.per" = 'Prop.2perhouse')) %>% 
  gather(type, vv, -vars) %>% 
  mutate( type = factor(type, labels = c('Attached', 'Not Attached') ),
          positive = factor(sign(vv), labels = c( 'Negative', 'Positive') ) )

@@

des.cl1 %>% 
  spread(vars,value) %>% 
  select(Q25, QCE2, Q7E, Q3B, Q8D, Q8A, Q15AA, Q7L, Q9, Q3A, Q15AB, Q6A, Q3C, Q6, Q7I, Q7F, Q7K, Q8F, Q7M, Q7D, QCE1, Q7A, Q7B, Q7C, Q8C, Q8E, Q8B, Q7H, Q18, Q7G, Q24,YEAR,cl.id) %>% 
  rename( Family = Q25, Refer = QCE2, Perfect = Q7E, Children = Q3B, Leader = Q8D, Proud = Q8A, Lead.Int. = Q15AA, Talented = Q7L, Job = Q9, Meet.People = Q3A, `5year.ahead` = Q15AB, School = Q6A, Reputation = Q3C, `5year.ago` = Q6, Care = Q7I, Senior = Q7F, Economy = Q7K, Satisfaction = Q8F, Health = Q7M, Find.Job = Q7D, Parks = QCE1, 
Beauty = Q7A, Roads = Q7B, Housing = Q7C, Night.Life = Q8C, Minorities = Q8E, Inmigrants = Q8B, Gay = Q7H, Safe = Q18, Colleges = Q7G, Friends = Q24, Clusters = cl.id) %>% 
 gather(vars, value, -Clusters,-YEAR) %>% 
  ggplot(aes(x = vars, y = value, color = Clusters, shape = Clusters), size = I(3)) + labs(x = "", y = "") +  geom_point(size = I(3))  + geom_line(aes(group = Clusters)) + 
  facet_wrap(~YEAR, nrow = 3) + theme(axis.text.x = element_text(angle = 90, size = I(15)), legend.position = 'bottom' ) + scale_color_brewer(type = 'qual', palette = 'Paired')

@@

<<moving, dependson='data', echo=FALSE,results='asis', cache=FALSE>>=
soul %>% 
  mutate(Q5 = recode_factor(Q5, "(DK)" = "Non Response", 
    "(Refused)" = "Non Response",
    "Move outside of (answer from Sc) but stay in the state" = "Move from your neighborhood",
    "Move outside of this communitybut stay in the state" = "Move from your neighborhood",
    "Move to another city and state altogether" = "Move from your neighborhood",
    "Move to another neighborhood in (answer from Sc)" = "Move from your neighborhood", 
    "Move to another neighborhood in this community" = "Move from your neighborhood")) %>%  
  filter(!is.na(PROJWT)) %>% 
  mutate(pr = PROJWT/3)  %>% 
  svydesign(ids =~1, strata =~QSB, weights =~pr, data = .) %>% 
  svyby(~Q5,~CCEGRP2, design = ., svymean,keep.var = FALSE, na.rm = T) %>% 
  ftable() %>% data.frame() %>% mutate(Freq = Freq*100) %>% 
  mutate( Var2 = gsub('statistic.Q5', '', Var2) ) %>% 
  spread(CCEGRP2, Freq) %>%  
  xtable(caption = 'Willingness to move outside your neighborhood', label = 'move') %>% 
  print(caption.placement = 'top')
